\cvsection{Outreach}{

    \cvitem{Astronomy on Tap: Dark Energy in the era of DESI}{May 2024}{
        Public talk at a Seattle brewery on Baryon Acoustic Oscillations, the Dark Energy Spectroscopic Instrument (DESI), and theories of Dark Energy.
    }
    
    \cvitem{Astronomy on Tap: Before the Big Bang}{Apr 2023}{
        Public talk at a Seattle brewery on the CMB, inflation, primordial perturbations, and the potential for an inflationary multiverse.
    }

    \cvitem{Outreach at ScioŠkola Praha 11}{May 2022}{
        Taught a class of Czech middle school students about Earth's magnetic field, the solar wind, and how the environment of Mars was impacted by the loss of its magnetic field.
    }
    
    \cvitem{Graduate Student Q\&A Panel, UC Berkeley}{Jul 2021}{
        Spoke on panel serving undergraduate students.
        Discussed aspects of graduate student life and research, with an emphasis on work-life balance, and navigating academic spaces as a queer person.
    }
    
    \cvitem{STEM Pals Organizer \& Pedagogical Simulation Lead}{2021}{
        Helped launch a STEM outreach program at the University of Washington.
        Designed interactive simulations to teach high school students how simulations allow researchers to study complex systems.
    }

    \cvitem{Duke University Teaching Observatory}{2018-2019}{
        Held star parties for members of the public, using telescopes to observe nebulae, star clusters, and planets.
    }

    \cvitem{Queer in Research Discussion Panel}{Oct 2018}{
        Spoke on panel discussing experiences as a queer person in STEM.
        Gave advice on how to find queer-friendly research groups and how to build queer support systems in a professional context.
    }

    \cvitem{Public Lecture: Where Did We Come From and Are We Alone -- Cosmic Origins and the Search for Life}{Jan 2018}{
        Public lecture for undergraduates at Duke University explaining the standard model of cosmology, the search for life in the solar system and on exoplanets.
    }

}