\section{Publications}

As of September 2025, I have (co-)authored 12 papers, with a total of 80 citations and an h-index of 5. \vspace{2mm}

\textbf{First and Second Author:}
\begin{etaremune}
\item \href{https://ui.adsabs.harvard.edu/abs/2025arXiv250306016C}{\textit{Quantifying the Impact of LSST $u$-band Survey Strategy on Photometric Redshift Estimation and the Detection of Lyman-break Galaxies}} \\ 
\textbf{Crenshaw J. F.}, Leistedt B., Graham M. L., Payerne C., et al. (2025) 
arXiv:2503.06016 

\item \href{https://ui.adsabs.harvard.edu/abs/2024AJ....168...80C}{\textit{Probabilistic Forward Modeling of Galaxy Catalogs with Normalizing Flows}} \\ 
\textbf{Crenshaw J. F.}, Kalmbach J. B., Gagliano A., Yan Z., et al. (2024) 
AJ 168 80 

\item \href{https://ui.adsabs.harvard.edu/abs/2024AJ....167...86C}{\textit{Using AI for Wave-front Estimation with the Rubin Observatory Active Optics System}} \\ 
\textbf{Crenshaw J. F.}, Connolly A. J., Meyers J. E., Kalmbach J. B., et al. (2024) 
AJ 167 86 

\item \href{https://ui.adsabs.harvard.edu/abs/2020AJ....160..191C}{\textit{Learning Spectral Templates for Photometric Redshift Estimation from Broadband Photometry}} \\ 
\textbf{Crenshaw J. F.}, Connolly A. J., et al. (2020) 
AJ 160 191 

\end{etaremune}

\textbf{Co-Author with Major Contributions:}
\begin{etaremune}
\item \href{https://ui.adsabs.harvard.edu/abs/2025arXiv250502928T}{\textit{Redshift Assessment Infrastructure Layers (RAIL): Rubin-era photometric redshift stress-testing and at-scale production}} \\ 
The RAIL Team, including \textbf{Crenshaw J. F.} (2025) 
arXiv:2505.02928 

\item \href{https://ui.adsabs.harvard.edu/abs/2025rubn.rept...35C}{\textit{SITCOMTN-154: Initial studies of photometric redshifts with LSSTComCam from DP1}} \\ 
Charles E., \textbf{Crenshaw J. F.}, Zhang T., Schmidt S., et al. (2025) 

\item \href{https://ui.adsabs.harvard.edu/abs/2024MNRAS.535.2970H}{\textit{Impact of survey spatial variability on galaxy redshift distributions and the cosmological 3 × 2-point statistics for the Rubin Legacy Survey of Space and Time (LSST)}} \\ 
Hang Q., Joachimi B., Charles E., \textbf{Crenshaw J. F.}, et al. (2024) 
MNRAS 535 2970 

\item \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...974..108M}{\textit{The Active Optics System on the Vera C. Rubin Observatory: Optimal Control of Degeneracy among the Large Number of Degrees of Freedom}} \\ 
Megias Homar G., Kahn S. M., Meyers J. M., \textbf{Crenshaw J. F.}, et al. (2024) 
ApJ 974 108 

\item \href{https://ui.adsabs.harvard.edu/abs/2024ApJ...967L...6M}{\textit{Improving Photometric Redshift Estimates with Training Sample Augmentation}} \\ 
Moskowitz I., Gawiser E., \textbf{Crenshaw J. F.}, Andrews B. H., et al. (2024) 
ApJ 967 L6 

\item \href{https://ui.adsabs.harvard.edu/abs/2023MNRAS.520.2887L}{\textit{The simulated catalogue of optical transients and correlated hosts (SCOTCH)}} \\ 
Lokken M., Gagliano A., Narayan G., et al., including \textbf{Crenshaw J. F.} (2023) 
MNRAS 520 2887 

\item \href{https://ui.adsabs.harvard.edu/abs/2022PASP..134d4501S}{\textit{The Sensitivity of GPz Estimates of Photo-z Posterior PDFs to Realistically Complex Training Set Imperfections}} \\ 
Stylianou N., Malz A. I., Hatfield P., \textbf{Crenshaw J. F.}, et al. (2022) 
PASP 134 044501 

\item \href{https://ui.adsabs.harvard.edu/abs/2021arXiv210408229M}{\textit{An information-based metric for observing strategy optimization, demonstrated in the context of photometric redshifts with applications to cosmology}} \\ 
Malz A. I., Lanusse F., \textbf{Crenshaw J. F.}, Graham M. L., et al. (2021) 
arXiv:2104.08229 

\end{etaremune}



