\cvsection{Leadership\\\& Service}{

    \cvitem{DESC Lyman-break Galaxy Topical Team Leader}{2024-present}{
        Created and leading the Lyman-break Galaxy (LBG) topical team of the Dark Energy Science Collaboration (DESC), focusing on performing precision cosmology with high-redshift galaxies in the range $2 < z < 6$.
    }

    \cvitem{Co-chair of the DESC Equity, Diversity, and Inclusion Committee}{2023-present}{
        Leading the Equity, Diversity, and Inclusion (EDI) committee of the Dark Energy Science Collaboration (DESC), including efforts to make DESC resources more accessible to new members, develop EDI guidelines for DESC meetings, and expand safety resources for meeting attendees covering issues such as racism, transphobia, homophobia, access to reproductive care, and mental health.
    }

    \cvitem{Rubin Observatory Science Collaborations EDI Committee}{2023-present}{
        Serving as the Dark Energy Science Collaboration (DESC) representative on the Equity, Diversity, and Inclusion committee of the Vera C. Rubin Observatory's council of Science Collaborations.
    }

    \cvitem{DUSC Cosmology and Astroparticle Group Leader}{2022-present}{
        Leading the cosmology and astroparticle group meetings of the Dark Universe Science Center (DUSC) at the University of Washington.
        Duties include setting the agenda, inviting speakers, and organizing events.
    }

    %\cvitem{University of Washington Astronomy Journal Club}{2023-present}{
    %    Leading the weekly journal club of the University of Washington Astronomy Department.
    %}

    \cvitem{Rubin Community Workshop Science Organizing Committee}{2023-2024}{
        Setting the science agenda and inviting speakers for the 2023 and 2024 Rubin Observatory Community Workshops.
    }

    %\cvitem{DiRAC Machine Learning Group Leader}{2022-2023}{
    %    Leading the machine learning group of the DiRAC institute at the University of Washington.
    %    Duties include setting the agenda and inviting speakers.
    %}

    \cvitem{DESC Collaboration Meeting Science Organizing Committee}{2022-2023}{
        Planned the Winter 2023 meeting of the Dark Energy Science Collaboration (DESC), with a focus on the poster session, events for early career researchers, and the DESC spokesperson election.
    }

    \cvitem{AAS Software Carpentry Workshop Volunteer}{Jan 2023}{
        Assisted instruction in command line and Python programming in the Software Carpentry Workshop at the 241st meeting of the American Astronomical Society, in Seattle, WA.
    }

    %\cvitem{University of Washington Academic Grievance Committee}{2022}{
    %    Served on a committee including faculty and deans, adjudicating academic grievance cases brought forward by graduate students.
    %}

    \cvitem{Physics Undergraduate Reading Course Leadership Committee}{2022}{
        Organized reading course for undergraduates, including reviewing student applications, verifying progress during the term, and hosting final presentations.
    }

    %\cvitem{Photo-z Commissioning Session Organizer}{Aug 2022}{
    %    Organized the Photo-z Commissioning Session at the 2022 Rubin Observatory Project and Community Workshop in Tucson, AZ.
    %    Work included planning the session, inviting speakers, and facilitating group discussion.
    %}

    %\cvitem{Snowmass 2021 Summer Study A/V Co-coordinator}{Jul 2022}{
    %    Coordinated audio/visual equipment for the hyrbrid Snowmass 2021 Summer Study in Seattle, Washington.
    %    Work included determining needs, securing and setting up equipment, and training volunteers how to use the equipment.
    %}

    \cvitem{Physicists for Inclusion and Equity Officer}{2020-2021}{
        Lead group in the University of Washington Physics Department, with a focus on providing community and programming for underrepresented groups in physics.
    }

}