\cvsection{Software}{

    \cvitem{PZFlow: Probabilistic modeling of tabular data with normalizing flows}{}{
        Creator and lead developer.
        Python package for efficient, high-dimensional joint density estimation and generative modeling of any tabular data.
        \github{https://github.com/jfcrenshaw/pzflow}
        \pypi{https://pypi.org/project/pzflow/}
    }

    \cvitem{PhotErr: Photometric error model for astronomical imaging surveys}{}{
        Creator and lead developer. 
        Python package for estimating photometric errors for point and extended sources observed in astronomical imaging surveys, including the Rubin, Euclid, and Roman observatories.
        \github{https://github.com/jfcrenshaw/photerr}
        \pypi{https://pypi.org/project/photerr/}
    }

    \cvitem{RAIL: Redshift Assessment Infrastructure Layers}{}{
        Contributing developer.
        Python package for photo-z estimation and evaluation on large scale data.
        I lead development of the galaxy catalog and systematic error forward modeling framework.
        \github{https://github.com/LSSTDESC/RAIL}
        \pypi{https://pypi.org/project/pz-rail/}
    }

    \cvitem{ts-wep: Wavefront estimation for the Rubin Observatory Active Optics System}{}{
        Contributing developer.
        Python package that infers the optical wavefront using out-of-focus images from Rubin's Curvature Wavefront Sensors.
        I contribute to the wavefront estimation algorithms, and am leading the development of deep learning methods for wavefront estimation.
        \github{https://github.com/lsst-ts/ts\_wep}
    }
    
}